Measurement Bias from Address Aliasing

### 2014-05-07 paper.tex
Add conv table

\documentclass[a4paper,10pt,twocolumn,twoside]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{listings}
\usepackage{authblk}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}

@@

\pgfplotstableread{bin/convolution.dat}{\convolutiontable}
\begin{figure}[t]
  \caption{Cycle and alias counts for different offsets between input and output arrays in Listing~\ref{lst:conv}. Offset 0 means equal 12 bit address suffix, which is default behavior for mmap allocations. Array size $n=2^{20}$, compiled with -O3. }
  \label{fig:heapalias}
  \begin{tikzpicture}
    \begin{axis}[
        font = \small,
        xlabel=Relative offset in \lstinline!sizeof(float)! bytes,
        cycle list name=black white
      ]
      \addplot table[x expr = \thisrowno{0}, y = cycles:u] \convolutiontable ;
      \addplot table[x expr = \thisrowno{0}, y = r0107:u ] \convolutiontable ;
      \addlegendentry{cycles:u} ;
      \addlegendentry{r0107:u} ;
    \end{axis}
  \end{tikzpicture}
\end{figure}

@@

>>>>

\documentclass[a4paper,10pt,twocolumn,twoside]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{listings}
\usepackage{authblk}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{rotating}

@@

% Plot of cycles vs alias for estimated cost of O3 convolution
\pgfplotstableread{bin/conv-all-estimate.dat}{\convolutiontable}
\begin{figure}[t]
  \caption{Cycle and alias counts for different offsets between input and output arrays in Listing~\ref{lst:conv}. Offset 0 means equal 12 bit address suffix, which is default behavior for mmap allocations. Array size $n=2^{20}$, compiled with -O3. }
  \label{fig:heapalias}
  \begin{tikzpicture}
    \begin{axis}[
        font = \small,
        xlabel=Relative offset in \lstinline!sizeof(float)! bytes,
        cycle list name=black white
      ]
      \addplot table[x expr = \thisrowno{0}, y = cycles:u] \convolutiontable ;
      \addplot table[x expr = \thisrowno{0}, y = r0107:u ] \convolutiontable ;
      \addlegendentry{cycles:u} ;
      \addlegendentry{r0107:u} ;
    \end{axis}
  \end{tikzpicture}
\end{figure}

@@

% Table with detailed performance data, estimated for O3
\pgfplotstabletranspose[
  col sep=comma,
  columns={n, cycles:u,r0107:u,r02a3:u,r01a2:u,r05a3:u,r04a2:u,r20a1:u,r0860:u,r0160:u,r2049:u,r6049:u},
  colnames from=n % Automapped to new 'colnames' column
  ]\loadedtable{bin/conv-all-estimate.dat}

\begin{sidewaystable*}[p]
  \caption{Most interesting performance counters for O3 convolution code, estimated cost accounting for constant overhead of heap allocation in main. (see /resources for full table)}
  \label{tab:convstats}
  \pgfkeys{/pgf/number format/.cd,int trunc} % Output whole numbers
  \pgfplotstabletypeset[
    font=\normalsize,
    columns={[index]0, [index]1, [index]2, [index]3, [index]4, [index]5, [index]11, [index]21}, % Select interesting offsets
    columns/colnames/.style={string type,column name={}, column type={l}},
    columns/colnames/.append style={string replace={cycles:u}{Cycles}}, % Pretty print counter mnemonics
    columns/colnames/.append style={string replace={r0107:u}{Alias}},
    columns/colnames/.append style={string replace={r02a3:u}{cycle_activity.cycles_ldm_pending}},
    columns/colnames/.append style={string replace={r01a2:u}{resource_stalls.any}},
    columns/colnames/.append style={string replace={r05a3:u}{cycle_activity.stalls_l2_pending}},
    columns/colnames/.append style={string replace={r04a2:u}{resource_stalls.rs}},
    columns/colnames/.append style={string replace={r20a1:u}{uops_executed_port.port_5}},
    columns/colnames/.append style={string replace={r0860:u}{offcore_requests_outstanding.all_data_rd}},
    columns/colnames/.append style={string replace={r0160:u}{offcore_requests_outstanding.demand_data_rd}},
    columns/colnames/.append style={string replace={r2049:u}{dtlb_store_misses.stlb_hit_4k}},
    columns/colnames/.append style={string replace={r6049:u}{dtlb_store_misses.stlb_hit}},
    every head row/.style={before row=\toprule, after row=\midrule},
    every last row/.style={after row=\bottomrule}
    ]{\loadedtable}
\end{sidewaystable*}
